Automated discovery of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex

% Brief summary of the paper
In this paper, we use symbolic regression to extract interpretable equations from the \ppd of a flexible model fitted to the catalog of GWs.
We show SR can discover equations which are similar to state-of-the-art phenomenological models.
On top of finding forms that have already been discovered,
our result also shed insights on an open question---whether there exist additional features other than the two prominent peaks in the primary mass distribution \cite{Tiwari:2021yvr}.
The additional suggest interpreting any additional features such as tapering of the continuum or wiggles between the two peaks can be tricky as their significance are unclear.

>>>>

% Brief summary of the paper
In this paper, we use symbolic regression to extract interpretable equations from the \ppd of a flexible model fitted to the catalog of GWs.
We show SR can discover equations which are similar to state-of-the-art phenomenological models.
On top of finding forms that have already been discovered,
our result also shed insights on an open question---whether there exist additional features other than the two prominent peaks in the primary mass distribution \cite{Tiwari:2021yvr}.
Since the highest complexity equation does not significantly improve the fitting accuracy, one should take caution when interpreting the tapering of the continuum or wiggles between the two peaks as their significance are unclear.
